Co-moving stars in \textsl{Gaia DR1}

### 2016-11-10 paper/ms.tex
Modify figure 4 graph visualization and caption

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/dist_networksize.pdf}
  \end{center}
  \caption{%
    Histogram of co-moving network sizes.
    \label{fig:hist_Nneighbors}}
\end{figure*}

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/graphviz_examples.pdf}
  \end{center}
  \caption{%
    Visualizations of a few example networks of co-moving pairs of stars.
    Each star (node) is marked as a red circle, and a line (edge) is drawn
    between two stars if they are co-moving by our selection criteria
    (see \S~\ref{sub:selection}). On left, we show the largest network
    found in this study corresponding to the Pleiades star cluster.
    \label{fig:graphviz_examples}}
\end{figure*}

@@

Once we have decided the co-moving pairs from the candidate pair list,
these pairs form an undirected graph where stars are nodes, and
edges between the nodes exist for co-moving pairs of stars.
A star may have multiple co-moving neighbors, and two stars may either
be directly or indirectly connected by a set of edges.
We divide the network into connected components\footnote{A connected component of an undirected graph $G$
is a subgraph of $G$ in which any two nodes are connected to each other by a path.
We use the term ``network'' loosely to refer to a graph or its connected components.},
and show the distribution of their sizes in Figure~\ref{fig:hist_Nneighbors}.
The most common are size 2 networks, which mean mutually exclusive co-moving
pairs. However, it is clear that there are many aggregates of co-moving stars
discovered by looking for co-moving pairs.
These aggregates are likely moving groups, OB associations or star clusters.
There are 4555 connected components among 10,606 unique stars.
The maximum size of connected components is 151.
We show this largest network along with four randomly selected
examples of networks with sizes greater than 4 in Figure~\ref{fig:graphviz_examples}.
The largest network corresponds to the Pleiades open cluster.
One particular star in this network, TYC 1799-272-1, has 94 directly connected
co-moving neighbors, and is located at the center of the network.

>>>>

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/dist_networksize.pdf}
  \end{center}
  \caption{%
    Histogram of the sizes of connected components.
    \label{fig:hist_ccsize}}
\end{figure*}

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/graphviz_examples.pdf}
  \end{center}
  \caption{%
    Visualizations of a few example connected components of co-moving pairs of stars.
    Each star (node) is marked as a red circle, and a line (edge) is drawn
    between two stars if they are co-moving by our selection criteria
    (see \S~\ref{sub:selection}). On left, we show the largest network
    found in this study corresponding to the Pleiades star cluster.
    On right, we show four examples of connected components with varying sizes.
    The connected component on the upper left panel with a size of 58 corresponds
    to NGC~2632, also known as the Beehive cluster.
    \label{fig:graphviz_examples}}
\end{figure*}

@@

Once we have decided the co-moving pairs from the candidate pair list,
these pairs form an undirected graph where stars are nodes, and
edges between the nodes exist for co-moving pairs of stars.
A star may have multiple co-moving neighbors, and two stars may either
be directly or indirectly connected by a set of edges.
We divide the network into connected components\footnote{A connected component of an undirected graph $G$
is a subgraph of $G$ in which any two nodes are connected to each other by a path.
We use the term ``network'' loosely to refer to a graph or its connected components.},
and show the distribution of their sizes in Figure~\ref{fig:hist_ccsize}.
The most common are size 2 networks, which mean mutually exclusive co-moving
pairs. However, it is clear that there are many aggregates of co-moving stars
discovered by looking for co-moving pairs.
These aggregates are likely moving groups, OB associations or star clusters.
There are 4555 connected components among 10,606 unique stars.
The maximum size of connected components is 151.
We show this largest network along with four randomly selected
examples of networks with sizes greater than 4 in Figure~\ref{fig:graphviz_examples}.
The largest network corresponds to the Pleiades open cluster.
One particular star in this network, TYC 1799-272-1, has 94 directly connected
co-moving neighbors, and is located at the center of the network.
